Anonymous provision of services via blockchain

### 2022-03-08 access.tex
update steps names

\noindent \textbf
{Step 5. Proof of provision publication}\label{step-5-proof-of-provision-publication}

@@

\noindent \textbf
{Step 6. Proof-of-provision notification}\label{step-6-proof-of-provision-notification}

@@

\noindent \textbf
{Step 1. Customer turn: deliver package}\label{step-1-deliver-package}

@@

  \item
    \(\sigma_{1, c, \mathrm{n}} = \sbullet\), the customer has risked its materials but has not paid anything, so we assume he is in a neutral position. One would argue that the customer has put effort into delivering the materials to the SP or that the sample is valuable. We assume that the sample without personal information is useless, and the effort to deliver the package is negligible.
  \item
    \(\sigma_{1, s, \mathrm{n}} = \sbullet\), the SP is in the neutral position as he did not put any effort also the package has not brought any value to the SP.
  \end{itemize}
\item
  Starting a dispute:

@@

\noindent \textbf
{Step 2. Customer turn: pay for invoice}\label{step-2-pay-for-invoice}

@@

\noindent \textbf
{Step 5. SP turn: publication of proof-of-provision}\label{step-5-publication-of-proof-of-provision}

@@

\noindent \textbf
{Step 7. Customer turn: result download}\label{step-7-retrieval-of-results}

>>>>

\noindent \textbf
{Step 5. Proof of provision}\label{step-5-proof-of-provision-publication}

@@

\noindent \textbf
{Step 6. Pull proof of provision}\label{step-6-proof-of-provision-notification}

@@

\noindent \textbf
{Step 1. Customer turn: package delivery}\label{step-1-deliver-package}

@@

  \item
    \(\sigma_{1, c, \mathrm{n}} = \sbullet\), the customer has risked its materials but has not paid anything, so we assume he is in a neutral position. One would argue that the customer has put effort into delivering the materials to the SP or that the sample is valuable. We assume that the sample without personal information is useless, and the effort to deliver the package is negligible.
  \item
    \(\sigma_{1, s, \mathrm{n}} = \sbullet\), the SP is in a neutral position as he did not put any effort, and the package has not brought any value to the SP.
  \end{itemize}
\item
  Starting a dispute:

@@

\noindent \textbf
{Step 2. Customer turn: payment}\label{step-2-pay-for-invoice}

@@

\noindent \textbf
{Step 5. SP turn: Proof of provision}\label{step-5-publication-of-proof-of-provision}

@@

\noindent \textbf
{Step 7. Customer turn: download result}\label{step-7-retrieval-of-results}
